Data Specialization for a Staged Lambda Calculus

### 2015-02-18 paper/figures/splitting-overview.tex
really simple pure2grnd pass
cleaning up figure captions

\textbf{Single-Output Pipelines:}

@@

	\hspace{4em} $\pipeS p l r$ is the single-output pipeline to be evaluated

@@

\textbf{Mutiple-Output Pipelines:}

@@

	\hspace{4em} $\pipeM c l r$ is the multi-output pipeline to be evaluated

@@

\begin{minipage}[t]{0.45\textwidth}
Splitting Terms: $(\colmix e A) \splitonesym \pipeM p l r$, where
\par \hspace{2em} $\colmix e A$ is the \lang\ input term to be split 
\par \hspace{2em} $\pipeM p l r$ is the resulting multi-output pipeline
\\
Masking Partial Values: $[\xi;v] \vsplito \mval i q$, where
\par \hspace{2em} $[\xi;v]$ is a partial value in \lang, resulting from $\redonesym$
\par \hspace{2em} $\mval i q$ is the resulting masked value
\end{minipage}
&

\begin{minipage}[t]{0.45\textwidth}
Splitting Terms: $(\coltwo e A) \splittwosym \pipeS p l r$, where 	
\par \hspace{2em} $\coltwo e A$ is the \lang\ input term to be split
\par \hspace{2em} $\pipeS p l r$ is the resulting single-output pipeline
\end{minipage}

@@

\put(14,75){\raisebox{-0.5ex}{\makebox[22 \unitlength]{$\colmix e A$}}}
\put(14,37){\raisebox{-0.5ex}{\makebox[22 \unitlength]{$[\xi,v]$}}}
\put(64,75){\raisebox{-0.5ex}{\makebox[22 \unitlength]{$\pipeM c l r$}}}
\put(64,37){\raisebox{-0.5ex}{\makebox[22 \unitlength]{$\mval i q$}}}

@@

\end{abstrsyn}
\caption{Overview of Splitting.}
\label{fig:splittingSummary}
\end{figure*}

>>>>

\textbf{Syntactically Separated Term with Stage \bbtwo\ Output:}

@@

	\hspace{4em} $\pipeS p l r$ is the syntactically separated term to be evaluated

@@

\textbf{Syntactically Separated Term with Multistage Output:}

@@

	\hspace{4em} $\pipeM c l r$ is the syntactically separated term to be evaluated

@@

\begin{minipage}[t]{0.45\textwidth}
Splitting Terms: $(\colmix e A) \splitonesym \pipeM p l r$, where
\par \hspace{2em} $\colmix e A$ is the \lang\ input term to be split 
\par \hspace{2em} $\pipeM p l r$ is the syntactically separated result
\\
Masking Partial Values: $[\xi;v] \vsplito \mval i q$, where
\par \hspace{2em} $[\xi;v]$ is a partial value in \lang, resulting from $\redonesym$
\par \hspace{2em} $\mval i q$ is the resulting masked value
\end{minipage}
&

\begin{minipage}[t]{0.45\textwidth}
Splitting Terms: $(\coltwo e A) \splittwosym \pipeS p l r$, where 	
\par \hspace{2em} $\coltwo e A$ is the \lang\ input term to be split
\par \hspace{2em} $\pipeS p l r$ is the syntactically separated result
\end{minipage}

@@

\put(14,75){\raisebox{-0.5ex}{\makebox[22 \unitlength]{$\colmix e A$}}}
\put(14,37){\raisebox{-0.5ex}{\makebox[22 \unitlength]{$[\xi;v]$}}}
\put(64,75){\raisebox{-0.5ex}{\makebox[22 \unitlength]{$\pipeM c l r$}}}
\put(64,37){\raisebox{-0.5ex}{\makebox[22 \unitlength]{$\mval i q$}}}

@@

\end{abstrsyn}
\caption{Overview of splitting.}
\label{fig:splittingSummary}
\end{figure*}
